\documentclass[12pt,a4paper]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{lmodern}

\definecolor{gold}{HTML}{D4AF37}
\definecolor{darkbg}{HTML}{0A0E14}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black
}

\begin{document}

% ─── Title block ─────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE\bfseries Spotly --- Project Features \& User Roles}\\[0.5em]
    {\large Luxury Venue Discovery and Booking Platform}\\[1em]
    \begin{tabular}{ll}
        \textbf{Course:}      & ISS296 --- Spring 2026 \\
        \textbf{Instructor:}  & Mr. Amine Ben Hassouna \\
        \textbf{Team:}        & Cyrine Krichen, Eya Sassi, \\
                              & Lina Khemiri, Youssef Ben Jemaa \\
    \end{tabular}
\end{center}

\vspace{1.5em}
\hrule
\vspace{1.5em}

% ─── 1. System Roles ──────────────────────────────────────────────────────────
\section{System Roles}

Spotly distinguishes four user roles. A user's role is derived at runtime from
their account relationship to venues and is never stored as a fixed field.

\vspace{0.5em}
\begin{tabularx}{\linewidth}{>{\bfseries}lX}
    \toprule
    Role & Description \\
    \midrule
    Guest &
        An unauthenticated visitor. Guests can browse the landing page,
        explore the venue discovery page, view individual venue profiles,
        and scan QR codes to read the digital menu. They cannot make
        reservations or access any role-specific dashboard. \\
    \addlinespace
    Client &
        An authenticated user who holds no venue ownership and is not
        assigned as staff. Clients can search and filter venues, complete
        the full booking flow, monitor their reservation status in real
        time, manage their bookings from their personal dashboard, and
        submit reviews after a completed visit. \\
    \addlinespace
    Admin &
        A user whose email address matches the \texttt{adminEmail} field
        of a \texttt{Venue} record. The admin has full control over their
        venue: they configure the floor plan, manage the menu, process
        reservation requests, moderate guest reviews, generate QR codes,
        and update venue identity settings. A user becomes an admin by
        completing the venue onboarding flow after registration. \\
    \addlinespace
    Staff &
        A user linked to a venue through a \texttt{VenueStaff} record
        (assigned by the admin). Staff operate the live floor: they check
        in arriving guests, record no-shows, create walk-in reservations,
        and acknowledge waiter calls triggered from tables. Staff can also
        access the admin area in a read-only operational capacity. \\
    \bottomrule
\end{tabularx}

% ─── 2. Features ──────────────────────────────────────────────────────────────
\section{Features}

Features \textbf{F1--F20} form the core application delivered in Phase~1.
Features \textbf{F21--F23} are AI-powered additions delivered in Phase~2.

% ── Phase 1 ──────────────────────────────────────────────────────────────────
\subsection{Phase 1 --- Core Features}

\textbf{F1 --- User Authentication.}
Covers the full identity lifecycle of a user in the system.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Register a new account with first name, last name, email and password.
    \item Log in with existing credentials; session is persisted in local storage.
    \item Log out and invalidate the current session.
\end{itemize}

\textbf{F2 --- Venue Discovery and Search.}
Enables users to find venues that match their interests.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Browse the full list of available venues.
    \item Search venues by name using a live search bar.
    \item Filter venues by activity type using tag pills.
\end{itemize}

\textbf{F3 --- Venue Public Profile.}
Presents a venue's complete identity to any visitor.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item View venue name, description, tagline, location, ambience tags,
          activities, dress code, and supported languages.
    \item Browse the venue photo slideshow.
    \item Read published guest reviews and overall rating.
\end{itemize}

\textbf{F4 --- Digital Menu.}
Provides a QR-accessible menu scoped to the guest's table environment.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Browse menu items organised by category (starters, mains, desserts,
          drinks).
    \item View item name, description, price, allergens, and tags.
    \item Display only items available in the scanned table's environment
          when environment-specific scoping is configured.
\end{itemize}

\textbf{F5 --- Booking: Environment Selection.}
First step of the booking flow.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item View all environments configured for the selected venue.
    \item Select an environment to continue to seat selection.
\end{itemize}

\textbf{F6 --- Booking: Seat and Table Selection.}
Second step of the booking flow.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item View the visual floor plan of the selected environment with
          live table availability derived from existing reservations.
    \item Select an available table or seat.
    \item Choose reservation date and time.
\end{itemize}

\textbf{F7 --- Reservation Submission.}
Third and final step of the booking flow.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Fill in reservation details: name, email, phone number, number
          of guests, and optional notes.
    \item Submit the reservation request for admin approval.
    \item A double-submit guard prevents accidental duplicate requests.
\end{itemize}

\textbf{F8 --- Real-Time Reservation Status Tracking.}
Keeps the client informed without requiring page refreshes.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Display an animated timeline: Submitted $\to$ Under Review
          $\to$ Decision.
    \item Receive live status updates via cross-tab storage events the
          moment the admin acts.
    \item Automatically navigate to the client dashboard on approval or
          rejection.
\end{itemize}

\textbf{F9 --- Client Dashboard and Reservation Management.}
Gives the client a personal space to manage their activity.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item View upcoming confirmed reservations.
    \item View past reservation history.
    \item Cancel a reservation that is still in a pending or confirmed state.
\end{itemize}

\textbf{F10 --- Guest Review Submission.}
Allows clients to share their experience after a visit.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Submit a star rating (1--5) and written review for a completed reservation.
    \item Review is immediately visible on the venue public profile.
\end{itemize}

\textbf{F11 --- Admin Venue Onboarding.}
Guides a new admin through the minimum setup required before accessing
the full admin panel.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Enter the venue name and core identity details.
    \item Create at least one environment to unlock the admin dashboard.
\end{itemize}

\textbf{F12 --- Admin Dashboard and Overview.}
Central hub for the admin after onboarding.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item View key statistics: total reservations, pending requests, revenue
          indicators.
    \item Navigate to all venue management sections via the admin sidebar.
    \item Dynamic time-of-day greeting personalised to the admin.
\end{itemize}

\textbf{F13 --- Floor Plan Builder.}
Visual editor for configuring environments and table layouts.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Create, rename, and delete environments.
    \item Define canvas dimensions (width and height) and environment shape.
    \item Add table and seat elements to the canvas; drag to reposition and
          resize.
    \item Set element label, capacity, shape, and rotation.
    \item Add non-seating decor elements.
    \item Delete elements with a constraint warning when active reservations
          exist.
\end{itemize}

\textbf{F14 --- Menu Management.}
Full CRUD control over the venue's menu.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Add, edit, and delete menu items.
    \item Toggle item availability (visible or hidden on the digital menu).
    \item Assign items to specific environments or make them venue-wide.
    \item Organise items by category: starters, mains, desserts, or drinks.
\end{itemize}

\textbf{F15 --- Reservation Queue Management.}
Admin workflow for processing incoming reservation requests.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item View all reservation requests with their current status.
    \item Filter by status (pending, confirmed, rejected, cancelled), date,
          and environment.
    \item Approve a reservation, changing its status to Confirmed.
    \item Reject a reservation with a confirmation dialog.
\end{itemize}

\textbf{F16 --- Guest Review Management.}
Admin-side moderation of guest reviews.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item View all guest reviews submitted for the venue.
    \item Hide a review so it no longer appears on the public profile.
    \item Restore a previously hidden review.
\end{itemize}

\textbf{F17 --- QR Code Generation.}
Produces scannable codes that link guests directly to the digital menu.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Generate a QR code for each table element in each environment.
    \item Display a preview and provide a download option.
\end{itemize}

\textbf{F18 --- Venue Identity and Settings.}
Comprehensive editor for the venue's public-facing identity.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Edit name, tagline, description, location, and venue type.
    \item Manage ambience tags, activities, dress code, and supported languages.
    \item Upload, reorder, and remove gallery photos for the hero slideshow.
    \item Configure opening hours per environment.
\end{itemize}

\textbf{F19 --- Staff Operations Dashboard.}
Real-time floor management interface for on-shift staff.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item View the live floor map for a selected shift date and environment.
    \item Check in an arriving guest and update reservation status to
          Checked-In.
    \item Mark a non-arriving guest as No-Show.
    \item Check out a departing guest and mark reservation as Completed.
    \item Create an instant walk-in reservation for unbooked guests.
\end{itemize}

\textbf{F20 --- Waiter Call System.}
Real-time table-to-staff signalling mechanism.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Trigger a waiter call from the digital menu page at any table.
    \item Staff dashboard receives live call alerts via cross-tab storage events.
    \item Staff acknowledges and dismisses calls from the floor map.
\end{itemize}

% ── Phase 2 ──────────────────────────────────────────────────────────────────
\subsection{Phase 2 --- AI-Powered Features}

\textbf{F21 --- AI Voice Booking.}
Removes form friction by letting clients speak their reservation intent.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Tap a microphone button on the home page and speak a natural language
          reservation request.
    \item AI extracts booking intent (venue, date, time, guest count, notes)
          and pre-fills the confirmation form.
    \item Navigate directly to the confirmation step with all fields ready.
\end{itemize}

\textbf{F22 --- AI Semantic Venue Discovery.}
Alternative discovery mode driven by natural language description.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Switch to Describe mode on the home page.
    \item Type a free-text description of the desired atmosphere or occasion.
    \item AI ranks matching venues by semantic relevance and shows a one-line
          reason per match.
\end{itemize}

\textbf{F23 --- AI Reservation Insights.}
On-demand analytical observations for venue administrators.
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
    \item Click Generate on the admin dashboard to send aggregated reservation
          statistics to the AI.
    \item Receive 3--5 actionable insights about booking patterns, peak hours,
          no-show rates, and cancellation trends.
    \item Insights are displayed with severity indicators (info, warning,
          success).
\end{itemize}

% ─── 3. Feature–Role Matrix ───────────────────────────────────────────────────
\section{Feature--Role Involvement Matrix}

\begin{longtable}{>{\bfseries}lp{5.5cm}cccc}
    \toprule
    ID & Feature & Guest & Client & Admin & Staff \\
    \midrule
    \endfirsthead
    \toprule
    ID & Feature & Guest & Client & Admin & Staff \\
    \midrule
    \endhead
    \midrule
    \multicolumn{6}{r}{\footnotesize Continued on next page\ldots} \\
    \endfoot
    \bottomrule
    \endlastfoot
    F1  & User Authentication              & \checkmark & \checkmark & \checkmark & \checkmark \\
    F2  & Venue Discovery and Search        & \checkmark & \checkmark &            &            \\
    F3  & Venue Public Profile              & \checkmark & \checkmark & \checkmark &            \\
    F4  & Digital Menu                      & \checkmark & \checkmark &            & \checkmark \\
    F5  & Booking: Environment Selection    &            & \checkmark &            &            \\
    F6  & Booking: Seat and Table Selection &            & \checkmark &            &            \\
    F7  & Reservation Submission            &            & \checkmark &            &            \\
    F8  & Real-Time Status Tracking         &            & \checkmark &            &            \\
    F9  & Client Dashboard                  &            & \checkmark &            &            \\
    F10 & Guest Review Submission           &            & \checkmark &            &            \\
    F11 & Admin Venue Onboarding            &            &            & \checkmark &            \\
    F12 & Admin Dashboard and Overview      &            &            & \checkmark &            \\
    F13 & Floor Plan Builder                &            &            & \checkmark &            \\
    F14 & Menu Management                   &            &            & \checkmark &            \\
    F15 & Reservation Queue Management      &            &            & \checkmark &            \\
    F16 & Guest Review Management           &            &            & \checkmark &            \\
    F17 & QR Code Generation                &            &            & \checkmark &            \\
    F18 & Venue Identity and Settings       &            &            & \checkmark &            \\
    F19 & Staff Operations Dashboard        &            &            & \checkmark & \checkmark \\
    F20 & Waiter Call System                & \checkmark & \checkmark &            & \checkmark \\
    \midrule
    F21 & AI Voice Booking                  &            & \checkmark &            &            \\
    F22 & AI Semantic Venue Discovery       &            & \checkmark &            &            \\
    F23 & AI Reservation Insights           &            &            & \checkmark &            \\
\end{longtable}

\end{document}
