\documentclass[12pt,a4paper]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{lmodern}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\hypersetup{colorlinks=true, linkcolor=black, urlcolor=black}

% Column type for wrapped, left-aligned content
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

\begin{document}

% ─── Title block ─────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE\bfseries Spotly --- Features Grouping}\\[0.5em]
    {\large Luxury Venue Discovery and Booking Platform}\\[1em]
    \begin{tabular}{ll}
        \textbf{Course:}      & ISS296 --- Spring 2026 \\
        \textbf{Instructor:}  & Mr. Amine Ben Hassouna \\
        \textbf{Team:}        & Cyrine Krichen, Eya Sassi, \\
                              & Lina Khemiri, Youssef Ben Jemaa \\
    \end{tabular}
\end{center}

\vspace{1.5em}
\hrule
\vspace{1.5em}

% ─── Introduction ────────────────────────────────────────────────────────────
This document maps each application feature to the data model entities it
involves. Feature IDs are as defined in the \emph{Project Features \& User
Roles} document. Entities correspond to the classes in the UML class diagram.

\vspace{1em}
Each row lists the feature identifier, its name, and all data model entities
that are created, read, updated, or deleted during the execution of that
feature.

% ─── Phase 1 --- Core Features ───────────────────────────────────────────────
\section{Phase 1 --- Core Features}

\begin{longtable}{>{\bfseries}l L{4.5cm} L{7.5cm}}
    \toprule
    ID & Feature Name & Entities Involved \\
    \midrule
    \endfirsthead
    \toprule
    ID & Feature Name & Entities Involved \\
    \midrule
    \endhead
    \midrule
    \multicolumn{3}{r}{\footnotesize Continued on next page\ldots} \\
    \endfoot
    \bottomrule
    \endlastfoot

    F1 &
    User Authentication &
    \textbf{User} ---
    A \texttt{User} record is created on registration. On login, the
    matching \texttt{User} is read and a session object is written to
    local storage. \\
    \addlinespace

    F2 &
    Venue Discovery and Search &
    \textbf{Venue} ---
    The full \texttt{VENUE\_LIST} is read and filtered client-side.
    No write operations occur. \\
    \addlinespace

    F3 &
    Venue Public Profile &
    \textbf{Venue}, \textbf{Environment}, \textbf{Review} ---
    The \texttt{Venue} record is read for identity details and the
    slideshow. \texttt{Environment} records are read to list available
    spaces. \texttt{Review} records are read to display the rating
    summary and guest feedback. \\
    \addlinespace

    F4 &
    Digital Menu &
    \textbf{Venue}, \textbf{MenuItem}, \textbf{Environment} ---
    The \texttt{Venue} and \texttt{Environment} records are read for
    context (venue name, environment name). \texttt{MenuItem} records
    are read and filtered by \texttt{environmentIds} to show the
    correct items for the scanned table. \\
    \addlinespace

    F5 &
    Booking: Environment Selection &
    \textbf{Venue}, \textbf{Environment} ---
    \texttt{Venue} is read to display the venue header.
    All \texttt{Environment} records for the venue are read to render
    the selection cards. \\
    \addlinespace

    F6 &
    Booking: Seat and Table Selection &
    \textbf{Environment}, \textbf{Reservation} ---
    The selected \texttt{Environment} (including its
    \texttt{FloorElement} list) is read to render the floor plan.
    Existing \texttt{Reservation} records are read to derive live
    table availability (available vs.\ reserved). \\
    \addlinespace

    F7 &
    Reservation Submission &
    \textbf{Reservation}, \textbf{ReservationLog} ---
    A new \texttt{Reservation} record is created with status
    \texttt{REQUESTED}. A corresponding \texttt{ReservationLog} entry
    is created to record the initial status transition. \\
    \addlinespace

    F8 &
    Real-Time Reservation Status Tracking &
    \textbf{Reservation} ---
    The target \texttt{Reservation} record is read and watched via
    the local storage \texttt{storage} event. The UI reacts to status
    changes (\texttt{REQUESTED} $\to$ \texttt{APPROVED} /
    \texttt{REJECTED}) without additional writes. \\
    \addlinespace

    F9 &
    Client Dashboard and Reservation Management &
    \textbf{Reservation}, \textbf{Review} ---
    All \texttt{Reservation} records for the current user are read and
    segmented into upcoming and past lists. On cancellation, the
    matching \texttt{Reservation} status is updated to
    \texttt{CANCELLED}. \texttt{Review} records are read to show which
    past visits have already been reviewed. \\
    \addlinespace

    F10 &
    Guest Review Submission &
    \textbf{Review}, \textbf{Reservation} ---
    A new \texttt{Review} record is created linked to the completed
    \texttt{Reservation}. The \texttt{Reservation} is read to verify
    eligibility (status must be \texttt{COMPLETED}). \\
    \addlinespace

    F11 &
    Admin Venue Onboarding &
    \textbf{Venue}, \textbf{Environment} ---
    A new \texttt{Venue} record is created (or an existing one is
    updated) with the admin's identity details. At least one
    \texttt{Environment} record is created to complete onboarding. \\
    \addlinespace

    F12 &
    Admin Dashboard and Overview &
    \textbf{Venue}, \textbf{Reservation}, \textbf{ReservationLog} ---
    The admin's \texttt{Venue} record is read for the greeting.
    \texttt{Reservation} records are aggregated to compute statistics.
    \texttt{ReservationLog} records are read for trend data. \\
    \addlinespace

    F13 &
    Floor Plan Builder &
    \textbf{Environment}, \textbf{FloorElement} ---
    \texttt{Environment} records are created, updated, and deleted.
    The embedded \texttt{FloorElement} array within each
    \texttt{Environment} is modified as elements are added, moved,
    resized, or removed. \\
    \addlinespace

    F14 &
    Menu Management &
    \textbf{MenuItem}, \textbf{Environment} ---
    \texttt{MenuItem} records are created, updated (name, price,
    description, tags, allergens, availability), and deleted.
    \texttt{Environment} records are read to populate the environment
    scope selector. \\
    \addlinespace

    F15 &
    Reservation Queue Management &
    \textbf{Reservation}, \textbf{ReservationLog} ---
    All \texttt{Reservation} records for the venue are read and
    filtered. On approval or rejection, the target
    \texttt{Reservation} status is updated and a new
    \texttt{ReservationLog} entry is created to record the admin
    action. \\
    \addlinespace

    F16 &
    Guest Review Management &
    \textbf{Review} ---
    All \texttt{Review} records for the venue are read. On moderation,
    the \texttt{status} field of the target \texttt{Review} is toggled
    between \texttt{VISIBLE} and \texttt{HIDDEN}. \\
    \addlinespace

    F17 &
    QR Code Generation &
    \textbf{Venue}, \textbf{Environment}, \textbf{FloorElement} ---
    The \texttt{Venue} and all its \texttt{Environment} records are
    read. The \texttt{FloorElement} list is traversed to generate one
    QR code per table element. No records are written. \\
    \addlinespace

    F18 &
    Venue Identity and Settings &
    \textbf{Venue} ---
    The admin's \texttt{Venue} record is read into the editor form.
    On save, the \texttt{Venue} record is updated with new identity
    fields, image URLs, and hour configurations. \\
    \addlinespace

    F19 &
    Staff Operations Dashboard &
    \textbf{Reservation}, \textbf{ReservationLog},
    \textbf{VenueStaff}, \textbf{WaiterCall} ---
    \texttt{VenueStaff} is read to verify access and determine the
    associated venue. \texttt{Reservation} records are read and
    filtered by date and environment for the floor map. Status
    transitions (check-in, check-out, no-show, walk-in) update the
    \texttt{Reservation} and create \texttt{ReservationLog} entries.
    \texttt{WaiterCall} records are read for live alerts and updated
    on acknowledgement. \\
    \addlinespace

    F20 &
    Waiter Call System &
    \textbf{WaiterCall}, \textbf{Environment} ---
    A new \texttt{WaiterCall} record is created when a guest taps
    the call button on the digital menu. The \texttt{Environment}
    record is read to populate the call with the environment name
    and element label. On staff acknowledgement, the
    \texttt{WaiterCall} status is updated to \texttt{acknowledged}. \\

\end{longtable}

% ─── Phase 2 --- AI Features ─────────────────────────────────────────────────
\section{Phase 2 --- AI-Powered Features}

\begin{longtable}{>{\bfseries}l L{4.5cm} L{7.5cm}}
    \toprule
    ID & Feature Name & Entities Involved \\
    \midrule
    \endfirsthead
    \toprule
    ID & Feature Name & Entities Involved \\
    \midrule
    \endhead
    \bottomrule
    \endlastfoot

    F21 &
    AI Voice Booking &
    \textbf{Reservation}, \textbf{Venue} ---
    \texttt{Venue} records are read and sent to the AI as context for
    venue matching. The AI-parsed result is used to pre-populate a new
    \texttt{Reservation} in the confirmation form, which is then
    submitted using the standard F7 flow. \\
    \addlinespace

    F22 &
    AI Semantic Venue Discovery &
    \textbf{Venue} ---
    The full \texttt{VENUE\_LIST} (id, name, description,
    ambienceTags, activities, dressCode) is read and forwarded to
    the AI. The AI returns a ranked list of venue IDs. No records are
    written. \\
    \addlinespace

    F23 &
    AI Reservation Insights &
    \textbf{Reservation}, \textbf{ReservationLog} ---
    \texttt{Reservation} records for the past 30~days are aggregated
    (totals, status breakdown, day-of-week distribution, hour
    distribution, average guest count). \texttt{ReservationLog}
    entries may be consulted for trend context. The aggregated
    statistics are forwarded to the AI; no records are written. \\

\end{longtable}

\end{document}
